---
title: "MA DMF Middle Ground"
author: "Randall Hughes"
date: "10/12/2017"
output: html_document
---
#Updated 18 October 2017, F.Schenck

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
mg = read.csv ("MG_restoration_data_180CT2017.csv", header=T)


#Shoot density - differences by identity and transect; number of discs as covariate
model = lm(Shoot.density~Diversity.Treatment+Identity + Number.of.discs + Transect , data=mg)
anova(model)
plot(Shoots.per.disc~Identity, data=mg)
```
Analysis of Variance Table

Response: Shoot.density
                    Df Sum Sq Mean Sq  F value    Pr(>F)    
Diversity.Treatment  1   83.9    83.9   1.5808   0.21528    
Identity             5  651.2   130.2   2.4541   0.04793 *  
Number.of.discs      1 7292.0  7292.0 137.4099 3.986e-15 ***
Transect             2  338.1   169.1   3.1860   0.05103 .  
Residuals           44 2335.0    53.1                       
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

```{r}
#Percent cover - differences by transect; number of discs as covariate
model = lm(Percent.cover~Diversity.Treatment+Identity + Number.of.discs + Transect , data=mg)
anova(model)
```

```{r}
#Canopy height - marginal differences by diversity (poly higher) and identity; number of discs as covariate (but not sure why it matters?)
model = lm(Canopy.ht~Diversity.Treatment+Identity + Number.of.discs + Transect , data=subset(mg, Canopy.ht > 0))
anova(model)
plot(Canopy.ht~Diversity.Treatment, data=subset(mg, Canopy.ht > 0))
plot(Canopy.ht~Identity, data=subset(mg, Canopy.ht > 0))
```
#With outlier (0 canopy ht) removed
Analysis of Variance Table

Response: Canopy.ht
                    Df Sum Sq Mean Sq F value   Pr(>F)   
Diversity.Treatment  1 1009.8 1009.84 10.7085 0.002107 **
Identity             5 2205.3  441.06  4.6770 0.001695 **
Number.of.discs      1  116.2  116.21  1.2323 0.273121   
Transect             2  579.8  289.89  3.0740 0.056519 . 
Residuals           43 4055.0   94.30                    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#Without outlier removed
Analysis of Variance Table

Response: Canopy.ht
                    Df Sum Sq Mean Sq F value   Pr(>F)   
Diversity.Treatment  1  550.4  550.41  3.7438 0.059448 . 
Identity             5 1689.2  337.83  2.2979 0.061185 . 
Number.of.discs      1 1334.4 1334.40  9.0764 0.004282 **
Transect             2  596.5  298.27  2.0288 0.143610   
Residuals           44 6468.8  147.02                    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

##Test Code
```{r}
forest.vector <- c(0,1,1,2,3)
```



